\section{Questions}
\label{sec:questions}

\subsection{Question importance}
\label{sec:qimportance}
The importance of a question determines how it will be weighed when computing mutual matches.  Three stars means that the question will have higher weighting. Two stars, the default selection, means that the question will have normal weighting. One star means that the question has lower weighting.  To set the importance of the question you tap on the star icons   under the Importance header. 

\subsection{Question category}
\label{sec:qcategory}
The category of a question is used to organize the related questions.  The categories can then have a numeric factor applied to them to increase their relevance in the template.  This means that questions are weighted related to their own category.  To set the category of the question, tap on the desired colour icon  .  The select category will have a lined border around its edges  .

\subsection{Question responses}
\label{sec:qresponses}
The responses for a question change based on the question type.  The three types of questions are  true-false, multiple choice, and multiple answer.  The true-false question type has two possible responses, intended for binary responses.  The multiple choice question type allows you to select a single answer for a question from a list of provided options. The multiple answer question type allows you to select multiple answers for a single question from a list of provided options. 

The multiple answer and multiple choice question types allows you to add or remove additional responses. Tap the Plus button   under the Response header to add a new response. Tap the remove button  to the left of a response to remove it.

\subsection{Ordering questions}
\label{sec:qordering}
You can reorder the questions in a template on the Template Builder page (Figure 4.4). In the questions list, tap down on a question that you need to be moved and drag the question to its intended position. 

\subsection{Question match criteria}
\label{sec:matchcriteria}
\Friending{} compares the answers to questions in questionnaires to determine a numerical score to perform matches.  The question match criteria defines how many points are awarded based on the two provided answers.   The You column represents the chosen answer, and the Star Ratings ( ) represent the points award if the comparison answer has chosen this.  

On the Question Builder pages (Figure 4.7) for each of the question types, you can select the Matching Segment ( ) of the segmentation control.   

With the Match Segment enabled, you can set the scoring properties of each matching comparison.  Tap on the checkbox in the You column to see the scoring values of the question.  The Star Ratings ( ) represent the score value if comparison question had that option set.  The values are as such: an empty star is 0, half star is 0.5, and a full star is 1.  The comparison score from comparing two questions is equal to the summation of all score values, divided by the best possible score value for the question.

In Figure 4.7, the multiple-choice question has four options.  Option \#2 is currently selected, which results in the Star Ratings showing the points yielded if the comparison question had selected that answer.  The choice of Option \#2 yields a full star, and half stars (or 0.5 points) are yielded for Option \#3 and \#4.   
